\vfill LiteCrypto

### 2014-12-12 paper/paper.tex
FIXED IT
Added references

CubeSat is a international collaborative project of over 40 educational systems and private firms. A CubeSat is a satellite that is 10 cm3 and with a mass of 1.33 kg. 

@@

PolySat is Cal Poly’s branch of CubeSat, and was established since 1999. Dr. Bellardo is the current advisor for PolySat. They have eight launched missions and three are currently in development. 

@@

Our library can not use transfer large amount of data between home base and the satellite. AX.25 speed limits on data are rarely higher than 9,600 bits/s and are usually 1,200 bits/s. The satellite also does not return an acknowledgement packet after successful retrieving a packet. Therefore, we are restricted on which scheme to use for our crypto library. Another issue is the connection time with the CubeSat is at most 15 minutes an hour due to the satellite orbiting the Earth. Therefore, we cannot use schemes that require a constant connection with the satellite. 

@@

CyaSSL is a lightweight SSL/TLS library. It advertised a special build called LeanPSK, which was an implementation of CyaSSL that could be built in as little as 20 kilobytes. LeanPSK is also 20 times smaller than OpenSSL, and uses 1 to 36 kilobytes of memory. This configuration required pre-shared keys. However, after creating the binary ourselves and using their library, we found it to be complicated to build and the binary ended up to be 57 kilobytes. That was above our binary size requirement so we looked for a different library to use. 

@@

The NaCl crypto library has all of the core operations needed to build our crypto library. NaCl advertises state of the art security, improves usability, and improved speed. However the full NaCl library is too large for us to use, so we found a smaller version of the NaCl library to use.

@@

TweetNaCl supports 25 of the C NaCl functions used by applications and fits into a 100 tweets. It is self contained library so it was easy to build. However, it did not have HMAC build into TweetNaCl so we ported it from the original NaCl library.

@@

Most typical applications use the -O2 flags for improved performance, but on a space limited platform, the -Os flag is more useful. The -Os flag enables all -O2 flags that typically do not increase size as well as performing more optimizations to reduce size. \cite{GCC} 

@@

\clearpage
%cite all the references from the bibtex you haven't explicitly cited
\nocite{*}
%break long urls with lots of hyphens
\def\UrlBreaks{\do\/\do-}

@@

\bibliography{paper}
\end{multicols}
\end{document}

>>>>

CubeSat is a international collaborative project of over 40 educational systems and private firms. A CubeSat is a satellite that is 10 $cm^{3}$ and with a mass of 1.33 kg. \cite{CubeSat}

@@

PolySat is Cal Poly’s branch of CubeSat, and was established since 1999. Dr. Bellardo is the current advisor for PolySat. They have eight launched missions and three are currently in development. \cite{PolySat}

@@

Our library can not use transfer large amount of data between home base and the satellite. AX.25 speed limits on data are rarely higher than 9,600 bits/s and are usually 1,200 bits/s. \cite{AX25} The satellite also does not return an acknowledgement packet after successful retrieving a packet. Therefore, we are restricted on which scheme to use for our crypto library. Another issue is the connection time with the CubeSat is at most 15 minutes an hour due to the satellite orbiting the Earth. Therefore, we cannot use schemes that require a constant connection with the satellite. 

@@

CyaSSL is a lightweight SSL/TLS library. It advertised a special build called LeanPSK, which was an implementation of CyaSSL that could be built in as little as 20 kilobytes. LeanPSK is also 20 times smaller than OpenSSL, and uses 1 to 36 kilobytes of memory. This configuration required pre-shared keys. \cite{CyaSSL} However, after creating the binary ourselves and using their library, we found it to be complicated to build and the binary ended up to be 57 kilobytes. That was above our binary size requirement so we looked for a different library to use. 

@@

The NaCl crypto library has all of the core operations needed to build our crypto library. NaCl advertises state of the art security, improves usability, and improved speed. However the full NaCl library is too large for us to use, so we found a smaller version of the NaCl library to use. \cite{NaCl}

@@

TweetNaCl supports 25 of the C NaCl functions used by applications and fits into a 100 tweets. It is self contained library so it was easy to build. \cite{TweetNaClPaper} However, it did not have HMAC build into TweetNaCl so we ported it from the original NaCl library.

@@

Most typical applications use the -O2 flags for improved performance, but on a space limited platform, the -Os flag is more useful. The -Os flag enables all -O2 flags that typically do not increase size as well as performing more optimizations to reduce size. \cite{GCCOP} 

@@

\end{multicols}
\clearpage
%cite all the references from the bibtex you haven't explicitly cited
\nocite{*}
%break long urls with lots of hyphens
\def\UrlBreaks{\do\/\do-}

@@

\bibliography{paper}
\end{document}
